---
title: "Analysis and Tables"
output: rmarkdown::latex_document
---

```{r include=FALSE, echo=FALSE}
# load packages
source("helper-packages.R")

# set the path
path <- "~/Desktop/honors-thesis-main/00-data/cleaned-data"

# load analysis data frame
df_analysis <-
  readRDS(glue("{path}/df-analysis.RDS"))

# load an analysis data frame for robustness check with closed restaurants
rc_df_analysis <-
  readRDS(glue("{path}/rc_df_analysis.RDS"))

# load crosswalks with joined districts
crosswalk <-
  readRDS(glue("{path}/election-data/clean_crosswalk.RDS"))

# load clean restaurant data with "closed" restaurants for robustness checks
openrice_robustness_check <-
  readRDS(glue("{path}/restaurant-data/openrice_robustness_check.RDS"))

# load analysis data frame for robustness check 3a: uncontested districts (all joined districts dropped)
rc3a_df_analysis <-
  readRDS(glue("{path}/df_rc3a_analysis.RDS"))

# load analysis data frame for robustness check
rc3b_df_analysis <-
  readRDS(glue("{path}/df_rc3b_analysis.RDS")) 

# load analysis data frame for alternative treatment var
df_analysis_raw_no <-
  readRDS(glue("{path}/df_analysis_raw_no.RDS"))
```


# MAIN ANALYSIS-----------------------------------------------------------------
# DiD models with two-way fixed effects

```{r}
# outcome: vote shares for pro-demo, continuous predictor
vote_shares_mod1 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)

# outcome: vote shares for pro-demo, binary predictor
vote_shares_mod2 <-
  felm(prop_votes_demo ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)
```



# bootstrap standard errors

# ```{r}
# # function for bootstrapping
# bootstrap_felm <- function(data, indices) {
#   boot_data <- data[indices, ] # resample with replacement
#   model <- felm(prop_votes_demo ~ prop_Yellow | year + fake_unit_id | 0 | fake_unit_id, data = boot_data)
#   return(coef(model)) # return the coefficient
# }
# 
# 
# set.seed(123) 
# bootstrap_indices <- lapply(1:1000, function(i) sample(nrow(df_analysis), 
#                                                        replace = TRUE))
# bootstrap_results <- lapply(bootstrap_indices, bootstrap_felm, 
#                             data = df_analysis)
# 
# # convert list of coefficients to a matrix 
# coef_matrix <- do.call(rbind, bootstrap_results)
# 
# # calculate standard errors
# bootstrapped_se <- apply(coef_matrix, 2, sd)
# 
# # the bootstrapped standard error for 'prop_Yellow'
# prop_Yellow_se <- bootstrapped_se['prop_Yellow']
# ```
# 
# 
# # bootstrapped standard errors for majority (binary variable)
# 
# ```{r}
# # function for bootstrapping
# bootstrap_felm <- function(data, indices) {
#   boot_data <- data[indices, ] # resample with replacement
#   model <- felm(prop_votes_demo ~ majority_yellow | year + fake_unit_id | 0 | fake_unit_id, data = boot_data)
#   return(coef(model)) # return the coefficient
# }
# 
# 
# set.seed(123) 
# bootstrap_indices <- lapply(1:1000, function(i) sample(nrow(df_analysis), replace = TRUE))
# bootstrap_results <- lapply(bootstrap_indices, bootstrap_felm, data = df_analysis)
# 
# # convert list of coefficients to a matrix 
# coef_matrix <- do.call(rbind, bootstrap_results)
# 
# # calculate standard errors
# bootstrapped_se <- apply(coef_matrix, 2, sd)
# 
# # bootstrapped standard error for 'majority_yellow'
# majority_yellow_se <- bootstrapped_se['majority_yellow']
# majority_yellow_se
# ```





```{r}
# outcome: vote shares for pro-Beijing, continuous predictor
vote_shares_mod3 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)

# outcome: vote shares for pro-Beijing, binary predictor
vote_shares_mod4 <-
  felm(prop_votes_est ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)
```

```{r}
# outcome: turnouts, continuous predictor
vote_shares_mod5 <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)

# outcome: turnouts, binary predictor
vote_shares_mod6 <-
  felm(sum_joined_dist_total ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)
```

# produce latex table
```{r}
panels <-
  list(vote_shares_mod1, vote_shares_mod2,
       vote_shares_mod3, vote_shares_mod4,
       vote_shares_mod5, vote_shares_mod6)

# formatting functions  
f1 <- function(x) format(round(x, 2), nsmall = 2)
f2 <- function(x) format(round(x, 0), big.mark = ",")

out <- modelsummary(
  panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("prop_Yellow" = 'Proportion of "Yellow" restaurants',
               "majority_yellow" = 'Majority of restaurants are "Yellow"'),
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  select(-c(part, statistic)) %>% 
  clean_names() %>%
  rows_insert(tibble(term = "Year FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y")) %>%
  rows_insert(tibble(term = "District FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y"))
  
# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 6)),
        col.names = linebreak(c("", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 10,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 2, "Vote shares: pro-Beijing" = 2, "Turnouts: total votes cast" = 2)) %>%    
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = TRUE)
```



# ROBUSTNESS CHECK: DIFFERENT NUMBERS OF JOINED DISTRICTS DROPPED---------------
# 1: huge joined districts
```{r}
# number of districts joined: 2, 4, 5, 6
x <- c(6, 12, 15, 18)

# drop all joined districts
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[1]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_all_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_all_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_all_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

# joined DCCs: 4
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[2]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_4_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_4_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_4_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

# joined DCCs: 5
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[3]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_5_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_5_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_5_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

# joined DCCs: 6
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[4]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_6_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_6_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_6_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)
```


# print the table for robustness check 1

```{r}
rc1_panels <-
  list(
    "Panel A: All joined districts excluded" = list(
      mod_rc1_all_votes_demo, mod_rc1_all_votes_est, mod_rc1_all_turnouts
    ),
    "Panel B: Joined DCCs >= 4 excluded" = list(
      mod_rc1_4_votes_demo, mod_rc1_4_votes_est, mod_rc1_4_turnouts
    ),
    "Panel C: Joined DCCs >= 5 excluded" = list(
      mod_rc1_5_votes_demo, mod_rc1_5_votes_est, mod_rc1_5_turnouts
    ),
    "Panel D: Joined DCCs >= 6 excluded" = list(
      mod_rc1_6_votes_demo, mod_rc1_6_votes_est, mod_rc1_6_turnouts
    )
  )

out <- modelsummary(
  rc1_panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("prop_Yellow" = 'Proportion of "Yellow" restaurants'),
  shape = "rbind",
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  clean_names() %>%
  rows_insert(tibble(x = "Year FE", x1 = "Y", x2 = "Y", x3 = "Y")) %>%
  rows_insert(tibble(x = "District FE", x1 = "Y", x2 = "Y", x3 = "Y"))

# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 3)),
        col.names = linebreak(c("", "(1)", "(2)", "(3)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 11,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 2, "Vote shares: pro-Beijing" = 2, "Turnouts: total votes cast" = 2)) %>%     
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = TRUE)
```




# ROBUSTNESS CHECK: CLOSED RESTAURANTS ADDED------------------------------------
# DiD models with two-way fixed effects


# table: summary stats
```{r}
openrice_closed <-
  openrice_robustness_check %>%
  filter(store_status == 0)

prop.table(table(openrice_closed$ideo_text))
```


```{r}
# outcome: vote shares for pro-demo, continuous predictor
vote_shares_mod1 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)

# outcome: vote shares for pro-demo, binary predictor
vote_shares_mod2 <-
  felm(prop_votes_demo ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)
```

```{r}
# outcome: vote shares for pro-Beijing, continuous predictor
vote_shares_mod3 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)

# outcome: vote shares for pro-Beijing, binary predictor
vote_shares_mod4 <-
  felm(prop_votes_est ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)
```

```{r}
# outcome: turnouts, continuous predictor
vote_shares_mod5 <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)

# outcome: turnouts, binary predictor
vote_shares_mod6 <-
  felm(sum_joined_dist_total ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)
```

# produce latex table
```{r}
panels <-
  list(vote_shares_mod1, vote_shares_mod2,
       vote_shares_mod3, vote_shares_mod4,
       vote_shares_mod5, vote_shares_mod6)

# formatting functions  
f1 <- function(x) format(round(x, 2), nsmall = 2)
f2 <- function(x) format(round(x, 0), big.mark = ",")

out <- modelsummary(
  panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("prop_Yellow" = 'Proportion of "Yellow" restaurants',
               "majority_yellow" = 'Majority of restaurants are "Yellow"'),
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  select(-c(part, statistic)) %>% 
  clean_names() %>%
  rows_insert(tibble(term = "Year FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y")) %>%
  rows_insert(tibble(term = "District FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y"))

# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 6)),
        col.names = linebreak(c("", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 10,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 2, "Vote shares: pro-Beijing" = 2, "Turnouts: total votes cast" = 2)) %>%    
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = TRUE)
```




# ROBUSTNESS CHECK: UNCONTESTED DISTRICTS ADDED---------------------------------

```{r}
# panels: all joined districts dropped
mod_rc3a_1 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3a_df_analysis)

mod_rc3a_2 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3a_df_analysis)


# panels: interpolated votes for those joined districts
mod_rc3b_3 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3b_df_analysis)

mod_rc3b_4 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3b_df_analysis)

```

# latex outputs:

```{r}
# formatting functions  
f1 <- function(x) format(round(x, 2), nsmall = 2)
f2 <- function(x) format(round(x, 0), big.mark = ",")


rc3_panels <- 
  list(
    "Panel A: All joined districts excluded" = list(
      mod_rc3a_1, mod_rc3a_2
    ),
    "Panel B: Votes for joined districts interpolated" = list(
      mod_rc3b_3, mod_rc3b_4
    )
  )

out <- modelsummary(
  rc3_panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("prop_Yellow" = 'Proportion of "Yellow" restaurants'),
  shape = "rbind",
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  clean_names() %>%
  rows_insert(tibble(x = "Year FE", x1 = "Y", x2 = "Y")) %>%
  rows_insert(tibble(x = "District FE", x1 = "Y", x2 = "Y"))

# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = TRUE,
        align = c("l", rep("c", 2)),
        col.names = linebreak(c("", "(1)", "(2)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 12,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 1, "Vote shares: pro-Beijing" = 1)) %>%    
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = TRUE)
```


# Power Analysis----------------------------------------------------------------

```{r}
df_analysis_no_geo <- 
  df_analysis %>%
  select(-grouped_geometry)


imputed_data <- mice(df_analysis_no_geo, m=5, method='pmm')
df_analysis_imputed <- complete(imputed_data, 1)
```


```{r}
set.seed(123)
# vote shares for pro-democracy candidates
# set the parameters from the output
# estimated_effect_size <- -0.06481 
# std_error <- 0.05876

# simulation parameters
# no. of obs
n <- 2000
n_simulations <- 1000
alpha <- 0.001

# initialize a vector to store p-values from each simulation
p_values <- c()

for (i in 1:n_simulations) {
  print(i)
  # Sample units
  sample_ids <- sample(1:nrow(df_analysis_imputed), size = n, replace = TRUE)
  
  simulated_model <- felm(prop_votes_demo ~ prop_Yellow | year + fake_unit_id | 0 | fake_unit_id, 
                          df_analysis_imputed[sample_ids,])
  p_values <- c(p_values, unname(simulated_model$pval))
}
print(mean(p_values))
plot(density(p_values))

#   #  sampling from observed prop_Yellow values
#   sampled_prop_Yellow <- sample(df_analysis_imputed$prop_Yellow, size = 1500, replace = TRUE)
#   
#   # sample to match the new sample size
#   sampled_year <- sample(df_analysis_imputed$year, size = 1500, replace = TRUE)
#   sampled_fake_unit_id <- sample(df_analysis_imputed$fake_unit_id, size = 1500, replace = TRUE)
# 
#   # assuming a simple linear effect and normal error for illustration
#   simulated_prop_votes_demo <- estimated_effect_size * sampled_prop_Yellow + rnorm(n, 0, std_error)
#   
#   
#   df_simulated <- data.frame(prop_votes_demo = simulated_prop_votes_demo, 
#                              prop_Yellow = sampled_prop_Yellow,
#                              year = sampled_year,  # Now using sampled_year
#                              fake_unit_id = sampled_fake_unit_id)  # Now using sampled_fake_unit_id
#   
#   # fit the data
#   simulated_model <- felm(prop_votes_demo ~ prop_Yellow | year + fake_unit_id | 0 | fake_unit_id, 
#                           df_simulated)
#   p_values[i] <- summary(simulated_model)$coefficients["prop_Yellow", "Pr(>|t|)"]
# }


```


# Outcome 1: Pro-democracy vote shares

```{r}
n_to_sample <- round(c(1008 * 0.1, 1008 * 0.5, 1008 * 1, 1008 * 1.5, 1008 * 2, 1008 * 2.5))
n_simulations <- 1000

# initialize an empty data frame to store results
results_df <- data.frame(sample_size = c(), p_value = c())

for (n in n_to_sample) {
  # initialize an empty vector
  p_values <- c()
  
  #print(i)
  
  for (i in 1:n_simulations) {
    print(i)
    # sample units
    sample_ids <- sample(1:nrow(df_analysis_imputed), size = n, replace = TRUE)
    
    simulated_model <- felm(prop_votes_demo ~ prop_Yellow | year + fake_unit_id | 0 | fake_unit_id, 
                            df_analysis_imputed[sample_ids,])
    p_values <- c(p_values, unname(simulated_model$pval))
  }
  
  # add results to the data frame 
  results_df <- rbind(results_df, data.frame(sample_size = rep(n, n_simulations), p_value = p_values))
}



```



```{r}
pa_pro_dem <-
  results_df %>%
  ggplot(aes(x = p_value)) +
  geom_density(alpha = 0.3, fill = "gold") +
  facet_wrap(~sample_size, scales = "free", 
             ncol = 3, nrow = 2,
             labeller = labeller(
               sample_size = function(x) paste("Simulated sample size =", x))
             ) + 
  labs(title = " ",
       x = "p-value",
       y = "Density") +
  theme_bw() +
  theme(
    strip.text.x = element_text(size = 12), 
    strip.background = element_rect(fill = "cornsilk2"),
    legend.position = "none"
  )
```



# Outcome 2: Pro-establishment vote shares

```{r}
n_to_sample <- round(c(1008 * 0.1, 1008 * 0.5, 1008 * 1, 1008 * 1.5, 1008 * 2, 1008 * 2.5))
n_simulations <- 1000

# initialize an empty data frame to store results
results_df <- data.frame(sample_size = c(), p_value = c())

for (n in n_to_sample) {
  # initialize an empty vector
  p_values <- c()
  
  print(i)
  
  for (i in 1:n_simulations) {
    print(i)
    # sample units
    sample_ids <- sample(1:nrow(df_analysis_imputed), size = n, replace = TRUE)
    
    simulated_model <- felm(prop_votes_est ~ prop_Yellow | year + fake_unit_id | 0 | fake_unit_id, 
                            df_analysis_imputed[sample_ids,])
    p_values <- c(p_values, unname(simulated_model$pval))
  }
  
  # add results to the data frame 
  results_df <- rbind(results_df, data.frame(sample_size = rep(n, n_simulations), p_value = p_values))
}

```



```{r}
pa_pro_est <-
  results_df %>%
  ggplot(aes(x = p_value)) +
  geom_density(alpha = 0.3, fill = "cornflowerblue") +
  facet_wrap(~sample_size, scales = "free", 
             ncol = 3, nrow = 2,
             labeller = labeller(
               sample_size = function(x) paste("Simulated sample size =", x))
             ) + 
  labs(title = " ",
       x = "p-value",
       y = "Density") +
  theme_bw() +
  theme(
    strip.text.x = element_text(size = 12), 
    strip.background = element_rect(fill = "aliceblue"),
    legend.position = "none"
  )

```


# Outcome 3: Turnouts

```{r}
n_to_sample <- round(c(1008 * 0.1, 1008 * 0.5, 1008 * 1, 1008 * 1.5, 1008 * 2, 1008 * 2.5))
n_simulations <- 1000

# initialize an empty data frame to store results
results_df <- data.frame(sample_size = c(), p_value = c())

for (n in n_to_sample) {
  # initialize an empty vector
  p_values <- c()
  
  print(i)
  
  for (i in 1:n_simulations) {
    print(i)
    # sample units
    sample_ids <- sample(1:nrow(df_analysis_imputed), size = n, replace = TRUE)
    
    simulated_model <- felm(sum_joined_dist_total ~ prop_Yellow | year + fake_unit_id | 0 | fake_unit_id, 
                            df_analysis_imputed[sample_ids,])
    p_values <- c(p_values, unname(simulated_model$pval))
  }
  
  # add results to the data frame 
  results_df <- rbind(results_df, data.frame(sample_size = rep(n, n_simulations), p_value = p_values))
}

```



```{r}
pa_turnouts <-
  results_df %>%
  ggplot(aes(x = p_value)) +
  geom_density(alpha = 0.3, fill = "cadetblue") +
  facet_wrap(~sample_size, scales = "free", 
             ncol = 3, nrow = 2,
             labeller = labeller(
               sample_size = function(x) paste("Simulated sample size =", x))
             ) + 
  labs(title = " ",
       x = "p-value",
       y = "Density") +
  theme_bw() +
  theme(
    strip.text.x = element_text(size = 12), 
    strip.background = element_rect(fill = "honeydew2"),
    legend.position = "none"
  )

```





