---
title: "Analysis and Tables"
output: rmarkdown::latex_document
---

```{r include=FALSE, echo=FALSE}
# load packages
source("helper-packages.R")

# set the path
path <- "~/Desktop/honors-thesis-main/00-data/cleaned-data"

# load analysis data frame
df_analysis <-
  readRDS(glue("{path}/df-analysis.RDS"))

# load an analysis data frame for robustness check with closed restaurants
rc_df_analysis <-
  readRDS(glue("{path}/rc_df_analysis.RDS"))

# load crosswalks with joined districts
crosswalk <-
  readRDS(glue("{path}/election-data/clean_crosswalk.RDS"))

# load clean restaurant data with "closed" restaurants for robustness checks
openrice_robustness_check <-
  readRDS(glue("{path}/restaurant-data/openrice_robustness_check.RDS"))

# load analysis data frame for robustness check 3a: uncontested districts (all joined districts dropped)
rc3a_df_analysis <-
  readRDS(glue("{path}/df_rc3a_analysis.RDS"))

# load 
rc3b_df_analysis <-
  readRDS(glue("{path}/df_rc3b_analysis.RDS")) 
```

# MAIN ANALYSIS-----------------------------------------------------------------
# DiD models with two-way fixed effects

```{r}
# outcome: vote shares for pro-demo, continuous predictor
vote_shares_mod1 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)

# outcome: vote shares for pro-demo, binary predictor
vote_shares_mod2 <-
  felm(prop_votes_demo ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)
```

```{r}
# outcome: vote shares for pro-Beijing, continuous predictor
vote_shares_mod3 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)

# outcome: vote shares for pro-Beijing, binary predictor
vote_shares_mod4 <-
  felm(prop_votes_est ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)
```

```{r}
# outcome: turnouts, continuous predictor
vote_shares_mod5 <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)

# outcome: turnouts, binary predictor
vote_shares_mod6 <-
  felm(sum_joined_dist_total ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis)
```

# produce latex table
```{r}
panels <-
  list(vote_shares_mod1, vote_shares_mod2,
       vote_shares_mod3, vote_shares_mod4,
       vote_shares_mod5, vote_shares_mod6)

# formatting functions  
f1 <- function(x) format(round(x, 2), nsmall = 2)
f2 <- function(x) format(round(x, 0), big.mark=",")

out <- modelsummary(
  panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("(Intercept)" = "(Intercept)",
               "prop_Yellow" = 'Proportion of "Yellow" restaurants',
               "majority_yellow" = 'Majority of restaurants is "Yellow"'),
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  select(-c(part, statistic)) %>% 
  clean_names() %>%
  rows_insert(tibble(term = "Year FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y")) %>%
  rows_insert(tibble(term = "District FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y"))
  
# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 6)),
        col.names = linebreak(c("", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 10,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 2, "Vote shares: pro-Beijing" = 2, "Turnouts: total votes cast" = 2)) %>%    
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = FALSE)
```




# ROBUSTNESS CHECK 1: DIFFERENT NUMBERS OF JOINED DISTRICTS DROPPED-------------
# 1: huge joined districts
```{r}
# number of districts joined: 2, 4, 5, 6
x <- c(6, 12, 15, 18)

# 2
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[1]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_all_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_all_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_all_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

# 4
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[2]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_4_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_4_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_4_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

# 5
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[3]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_5_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_5_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_5_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

# 6
joined_districts_to_drop <-
  crosswalk %>%
  group_by(fake_unit_id) %>%
  summarise(n_obs = n()) %>%
  filter(n_obs >= x[4]) %>%
  select(fake_unit_id)

df_analysis_dropped <-
  df_analysis %>%
  filter(!(fake_unit_id %in% joined_districts_to_drop$fake_unit_id))

mod_rc1_6_votes_demo <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_6_votes_est <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)

mod_rc1_6_turnouts <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = df_analysis_dropped)
```


# print the table for robustness check 1

```{r}
rc1_panels <-
  list(
    "Panel A: All fake districts dropped" = list(
      mod_rc1_all_votes_demo, mod_rc1_all_votes_est, mod_rc1_all_turnouts
    ),
    "Panel B: joined districts >= 4 dropped" = list(
      mod_rc1_4_votes_demo, mod_rc1_4_votes_est, mod_rc1_4_turnouts
    ),
    "Panel C: joined districts >= 5 dropped" = list(
      mod_rc1_5_votes_demo, mod_rc1_5_votes_est, mod_rc1_5_turnouts
    ),
    "Panel D: joined districts >= 6 dropped" = list(
      mod_rc1_6_votes_demo, mod_rc1_6_votes_est, mod_rc1_6_turnouts
    )
  )

out <- modelsummary(
  rc1_panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("(Intercept)" = "(Intercept)",
               "prop_Yellow" = 'Proportion of "Yellow" restaurants'),
  shape = "rbind",
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, F,
      "r.squared", "$R^2$", f1, F),
  output = "data.frame") %>% 
  clean_names() %>%
  rows_insert(tibble(x = "Year FE", x1 = "Y", x2 = "Y", x3 = "Y")) %>%
  rows_insert(tibble(x = "District FE", x1 = "Y", x2 = "Y", x3 = "Y"))

# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 3)),
        col.names = linebreak(c("", "(1)", "(2)", "(3)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 11,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 2, "Vote shares: pro-Beijing" = 2, "Turnouts: total votes cast" = 2)) %>%     
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = FALSE)
```




# ROBUSTNESS CHECK 2: CLOSED RESTAURANTS ADDED----------------------------------
# DiD models with two-way fixed effects


# table: summary stats
```{r}
openrice_closed <-
  openrice_robustness_check %>%
  filter(store_status == 0)

prop.table(table(openrice_closed$ideo_text))
```


```{r}
# outcome: vote shares for pro-demo, continuous predictor
vote_shares_mod1 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)

# outcome: vote shares for pro-demo, binary predictor
vote_shares_mod2 <-
  felm(prop_votes_demo ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)
```

```{r}
# outcome: vote shares for pro-Beijing, continuous predictor
vote_shares_mod3 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)

# outcome: vote shares for pro-Beijing, binary predictor
vote_shares_mod4 <-
  felm(prop_votes_est ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)
```

```{r}
# outcome: turnouts, continuous predictor
vote_shares_mod5 <-
  felm(sum_joined_dist_total ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)

# outcome: turnouts, binary predictor
vote_shares_mod6 <-
  felm(sum_joined_dist_total ~ majority_yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc_df_analysis)
```

# produce latex table
```{r}
panels <-
  list(vote_shares_mod1, vote_shares_mod2,
       vote_shares_mod3, vote_shares_mod4,
       vote_shares_mod5, vote_shares_mod6)

# formatting functions  
f1 <- function(x) format(round(x, 2), nsmall = 2)
f2 <- function(x) format(round(x, 0), big.mark = ",")

out <- modelsummary(
  panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("(Intercept)" = "(Intercept)",
               "prop_Yellow" = 'Proportion of "Yellow" restaurants',
               "majority_yellow" = 'Majority of restaurants is "Yellow"'),
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  select(-c(part, statistic)) %>% 
  clean_names() %>%
  rows_insert(tibble(term = "Year FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y")) %>%
  rows_insert(tibble(term = "District FE", x1 = "Y", x2 = "Y", x3 = "Y",
                     x4 = "Y", x5 = "Y", x6 = "Y"))
  
# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 6)),
        col.names = linebreak(c("", "(1)", "(2)", "(3)", "(4)", "(5)", "(6)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 10,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares: pro-democracy" = 2, "Vote shares: pro-Beijing" = 2, "Turnouts: total votes cast" = 2)) %>%    
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = FALSE)
```




# ROBUSTNESS CHECK 3: UNCONTESTED DISTRICTS ADDED-------------------------------

```{r}
# panels: all joined districts dropped
mod_rc3a_1 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3a_df_analysis)

mod_rc3a_2 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3a_df_analysis)


# panels: interpolated votes for those joined districts
mod_rc3b_3 <-
  felm(prop_votes_demo ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3b_df_analysis)

mod_rc3b_4 <-
  felm(prop_votes_est ~ prop_Yellow|year + fake_unit_id|0|fake_unit_id, 
       data = rc3b_df_analysis)

```

# latex outputs:

```{r}
# formatting functions  
f1 <- function(x) format(round(x, 2), nsmall = 2)
f2 <- function(x) format(round(x, 0), big.mark = ",")


rc3_panels <- 
  list(
    "Panel A: All joined districts dropped" = list(
      mod_rc3a_1, mod_rc3a_2
    ),
    "Panel B: Votes for joined districts interpolated" = list(
      mod_rc3b_3, mod_rc3b_4
    )
  )

out <- modelsummary(
  rc3_panels, 
  stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
  coef_map = c("(Intercept)" = "(Intercept)",
               "prop_Yellow" = 'Proportion of "Yellow" restaurants'),
  shape = "rbind",
  gof_map =
    tribble(
      ~raw, ~clean, ~fmt, ~omit,
      "nobs", "No. of obs.", f2, FALSE,
      "r.squared", "$R^2$", f1, FALSE),
  output = "data.frame") %>% 
  clean_names() %>%
  rows_insert(tibble(x = "Year FE", x1 = "Y", x2 = "Y")) %>%
  rows_insert(tibble(x = "District FE", x1 = "Y", x2 = "Y"))

# latex output  
out %>%
  kable("latex", 
        booktabs = TRUE, 
        escape = FALSE,
        align = c("l", rep("c", 2)),
        col.names = linebreak(c("", "(1)", "(2)"), align = "c"),
        linesep = "") %>% 
  kable_styling(
    font_size = 12,
    latex_options = "hold_position") %>% 
  add_header_above(header = c(" " = 1, "Vote shares for pro-democracy candidates" = 1, "Vote shares for pro-Beijing candidates" = 1)) %>%    
  footnote(general = c("*p<0.1; **p<0.05; ***p<0.01"),
           footnote_as_chunk = TRUE, 
           general_title = "",
           escape = FALSE)
```








