---
title: "Cleaning 2011 District Council Election"
author: "Jiayi Li"
date: "2022-12-31"
output: html_document
---
Purpose: to clean the election results of the 2011 HK District Council Election at the polling station level.
To-Do: 
 -- Merge all excel files [Done]
 -- Geocode the merged file in Python [Done]
 -- Check for bad coordinates [Done]
 -- Reorder columns [Done]
 
```{r}
# load packages
source("helper-packages.R")

# load raw data
  path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election/individual_stations"
  
# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("hk_2011_disco_", i),                                   
           rio::import(data_files[i]))
  }
  
# load candidate info
  path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election"
  
  party_2011_raw <- 
    rio::import(glue("{path}/stacked_party_candidate_info_2011_disco.csv")) 
  names(party_2011_raw) <- tolower(names(party_2011_raw))
```

# stack all files of election results

```{r}
# bind rows 
  hk_2011_dsc_raw <-
    # merge all loaded data sets
    do.call("rbind", mget(ls(pattern = "^hk_2011_disco_*")))

# reset index
  row.names(hk_2011_dsc_raw) <- NULL

# lower column names
  names(hk_2011_dsc_raw) <- tolower(names(hk_2011_dsc_raw))
```
 
# reshape and select the candidate data for matching

```{r}
# pivot wider
reshaped_hk_2011_disco_candid <-
  party_2011_raw %>%
  # note that NA in `candidate_number` indicates that 
  # that constituency was uncontested
  drop_na(candidate_number) %>%
  # recode NAs
  mutate(
    political_affiliations_english = 
      case_when(
        political_affiliations_english == "NA" ~ NA_character_,
        TRUE ~ as.character(political_affiliations_english)
      ),
    
    political_ideo = 
      case_when(
        political_ideo == "NA" ~ NA_character_,
        TRUE ~ as.character(political_ideo)
      ),
  ) %>%
  # select variables of interest
  select(district_code, candidate_number,
         candidate_name_eng, political_affiliations_english,
         political_ideo) %>%
  pivot_wider(
    id_cols = `district_code`,
    names_from = `candidate_number`,
    values_from = c(`candidate_name_eng`, `political_affiliations_english`,
                    `political_ideo`)
  )

# select constituency variables for matching
constituency_info <-
  party_2011_raw %>%
  select(district_code, district) %>%
  distinct(district_code, district)
```

# cleaning

```{r}
hk_2011_stacked_joined <-
  hk_2011_dsc_raw %>%
  # add constituency variables
  left_join(constituency_info, by = "district_code") %>%
  # convert district names to title case
  mutate(
    district = str_to_title(district)
  ) %>%
  # add party candidate
  left_join(reshaped_hk_2011_disco_candid, by = "district_code") %>%
  # convert to numeric
  mutate_at(c(9:12), as.numeric)
```

# reorder the columns 

```{r}
col_order <-
  c("district",
    "district_code",
    "district_name",
    "chinese_name",
    "station_code",
    "chinese_name_poll_station",
    "name_poll_station",
    "candidate_name_eng_1", "political_ideo_1", "votes_candidate_1", "political_affiliations_english_1",
    "candidate_name_eng_2", "political_ideo_2", "votes_candidate_2", "political_affiliations_english_2",
    "candidate_name_eng_3", "political_ideo_3", "votes_candidate_3", "political_affiliations_english_3",
    "candidate_name_eng_4", "political_ideo_4", "votes_candidate_4", "political_affiliations_english_4",
    "candidate_name_eng_5", "political_ideo_5", "votes_candidate_5", "political_affiliations_english_5",
    "candidate_name_eng_6", "political_ideo_6", "votes_candidate_6", "political_affiliations_english_6"
  )

# reorder the columns
not_geocoded_2011_dsc <- 
  hk_2011_stacked_joined[, col_order] 
```

# save a version for geocoding in Google Maps API

```{r}
write.csv(not_geocoded_2011_dsc, glue("{path}/clean_not_geocoded_2011_dsc.csv"),
          row.names = FALSE)
```

# clean the geocoded file

```{r}
# load the raw data
geocoded_disco_2011 <-
  read.csv(glue("{path}/geocoded_disco_2011.csv"),
           na.strings = c("", NA_character_))

# clean 
clean_geocoded_disco_2011 <-
  geocoded_disco_2011 %>%
  rename("ps_gmaps_coords" = gmaps_coords) %>%
  mutate(
    # remove brackets in the `ps_gmaps_coords` column
      ps_gmaps_coords = str_replace_all(ps_gmaps_coords, "\\[|\\]", "")
    ) %>%
    # separate the `gmaps_coords` column into two: lat and lon
    separate(ps_gmaps_coords, into = c("lat", "lon"), sep = ",", remove = FALSE) %>%
    # check for bad coordinates
    # Hong Kong SAR lies between Latitude 22째08' North and 22째35' North, 
    # Longitude 113째49' East and 114째31' East
    mutate(
      bad_coords =
        case_when(
          as.numeric(lat) < 22|as.numeric(lat) > 23|as.numeric(lon) < 113|as.numeric(lon) > 115 ~ "bad",
          TRUE ~ "good"
        )
    ) %>%
  # remove `bad names`
  select(-bad_names)
```

# save a version for correcting miscoded polling stations

```{r}
write.csv(clean_geocoded_disco_2011, glue("{path}/handcoding_clean_geocoded_2011_dsc.csv"),
          row.names = FALSE)
```

# randomly select a sample for auditing (drop `bad_coords` == bad)

```{r}
set.seed(123)
audit_10p_2011_disco <-
    clean_geocoded_disco_2011 %>%
    # drop those i manually corrected
    filter(bad_coords != "bad") %>%
    # sample ten percent of polling stations for auditing
    sample_n(45)
```

# standardize the column order for the hand-geocoded file

```{r}
# load the raw data
handgeocoded_2011_disco <-
  read.csv(glue("{path}/handcoded_cleaned_2011_disco.csv")) 

# final cleaning
final_clean_2011_disco <-
  handgeocoded_2011_disco %>%
  # reorder the columns
  relocate(ps_gmaps_coords, lat, lon, .after = name_poll_station) %>%
  # drop the coordinate verification column
  select(-bad_coords)
```

# save as csv

```{r}
write.csv(final_clean_2011_disco,
          "~/Desktop/honors-thesis-main/00-data/cleaned-data/election-data/final_clean_2011_disco.csv",
          row.names = FALSE)
```


 
