---
title: "Cleaning 2015 District Council Election"
author: "Jiayi Li"
date: "2022-09-13"
output: html_document
---
Purpose: to clean the election results of the 2015 HK District Council Election at the polling station level.
To-Do: 
- 09/13:
 -- Merge all excel files (done)
 -- Add a constituency column (done)
 -- Geocode the merged file in Python 
 -- Check for bad coordinates 
 -- Reorder columns 
 
```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and data

```{r}
# load packages
  source("helper-packages.R")

# load raw election data
  path <- "/Users/jiayili/Dropbox/senior-thesis/00-data/00-raw-data/election-data/2015_district_council_election/individual_stations/"
# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("hk_2015_disco_", i),                                   
           rio::import(data_files[i]))
  }
  
# load data with candidate names
  path_1 <- "/Users/jiayili/Dropbox/senior-thesis/00-data/00-raw-data/election-data/2015_district_council_election"
  candid_hk_2015_disco <-
    read.csv(glue("{path_1}/hk2015_district_election_candidate_shares.csv")) %>%
    # drop the index column
    select(-X)
```

# reshape the candidate data for matching

## Notes: "*" means uncontested --> dropped

```{r}
# pivot wider
reshaped_hk_2015_disco_candid <-
  candid_hk_2015_disco %>%
  pivot_wider(
    id_cols = `Constituency.Code`,
    names_from = c(`Candidate.Number`),
    values_from = `Name.of.Candidate`,
    names_prefix = "name_candid_"
  ) %>%
  select("district_code" = `Constituency.Code`, starts_with("name_candid_")) %>%
  # drop uncontested candidates
  select(-`name_candid_*`)
```

# stack counting results at the ps level and clean

```{r}
# bind rows 
  hk_2015_dsc_raw <-
    # merge all loaded data sets
    do.call("rbind", mget(ls(pattern = "^hk_2015_disco_*")))
# reset index
  row.names(hk_2015_dsc_raw) <- NULL
# lower column names
  names(hk_2015_dsc_raw) <- tolower(names(hk_2015_dsc_raw))
  
# clean
  clean_not_geocoded_2015_dsc <-
    hk_2015_dsc_raw %>%
    mutate(
      # add a constituency columns
      constituency = 
        case_when(
          str_detect(district_code, "A") ~ "Central & Western",
          str_detect(district_code, "B") ~ "Wan Chai",
          str_detect(district_code, "C") ~ "Eastern District",
          str_detect(district_code, "D") ~ "Southern District",
          str_detect(district_code, "E") ~ "Yau Tsim Mong District",
          str_detect(district_code, "F") ~ "Sham Shui Po",
          str_detect(district_code, "G") ~ "Kowloon City District",
          str_detect(district_code, "H") ~ "Wong Tai Sin District",
          str_detect(district_code, "J") ~ "Kwun Tong District",
          str_detect(district_code, "K") ~ "Tsuen Wan District",
          str_detect(district_code, "L") ~ "Tuen Mun District",
          str_detect(district_code, "M") ~ "Yuen Long District",
          str_detect(district_code, "N") ~ "North District",
          str_detect(district_code, "P") ~ "Tai Po District",
          str_detect(district_code, "Q") ~ "Sai Kung District",
          str_detect(district_code, "R") ~ "Sha Tin District",
          str_detect(district_code, "S") ~ "Kwai Tsing District",
          str_detect(district_code, "T") ~ "Islands District",
        ) 
    ) %>%
    # add candidate name columns
    left_join(reshaped_hk_2015_disco_candid, by = "district_code")
```

# save a version for geocoding in python

```{r}
write.csv(clean_not_geocoded_2015_dsc, "/Users/jiayili/Dropbox/senior-thesis/01-code/working-data/clean_not_geocoded_2015_dsc.csv")
```


