---
title: "Cleaning 2019 District Coucil Election"
author: "Jiayi Li"
date: "2022-08-23"
output: html_document
---
Purpose: to clean the election results of the 2019 HK District Council Election at the polling station level.
To-Do: 
- 08/23:
 -- Merge all excel files (done)
 -- Add a constituency column (done)
 -- Geocode the merged file in Python (done)
 -- Check for bad coordinates (done)
 -- Reorder columns (done)
 
```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and raw data

```{r}
# load packages
  source("helper-packages.R")

# load raw election data
  path <- "/Users/jiayili/Dropbox/senior-thesis/00-data/00-raw-data/election-data/2019_district_council_election/individual_stations/"
# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("hk_2019_disco_", i),                                   
           rio::import(data_files[i]))
  }
  
# load data with candidate names
  path_1 <- "/Users/jiayili/Dropbox/senior-thesis/00-data/00-raw-data/election-data/2019_district_council_election"
  candid_hk_2019_disco <-
    rio::import(glue("{path_1}/hk2019_district_election_candidate_shares.csv")) %>%
    # drop the index column
    select(-V1)

```

# reshape the candidate data for matching

```{r}
# pivot wider
reshaped_hk_2019_disco_candid <-
  candid_hk_2019_disco %>%
  pivot_wider(
    id_cols = `Constituency Code`,
    names_from = c(`Candidate Number`),
    values_from = `Name of Candidate`,
    names_prefix = "name_candid_"
  ) %>%
  select("district_code" = `Constituency Code`, starts_with("name_candid_"))
```

# stack counting results at the ps level and clean

```{r}
# bind rows 
  hk_2019_dsc_raw <-
    # merge all loaded data sets
    do.call("rbind", mget(ls(pattern = "^hk_2019_disco_*")))

# reset index
  row.names(hk_2019_dsc_raw) <- NULL

# lower column names
  names(hk_2019_dsc_raw) <- tolower(names(hk_2019_dsc_raw))
  
# clean
  clean_not_geocoded_2019_dsc <-
    hk_2019_dsc_raw %>%
    mutate(
      # add a constituency columns
      constituency = 
        case_when(
          str_detect(district_code, "A") ~ "Central & Western",
          str_detect(district_code, "B") ~ "Wan Chai",
          str_detect(district_code, "C") ~ "Eastern District",
          str_detect(district_code, "D") ~ "Southern District",
          str_detect(district_code, "E") ~ "Yau Tsim Mong District",
          str_detect(district_code, "F") ~ "Sham Shui Po",
          str_detect(district_code, "G") ~ "Kowloon City District",
          str_detect(district_code, "H") ~ "Wong Tai Sin District",
          str_detect(district_code, "J") ~ "Kwun Tong District",
          str_detect(district_code, "K") ~ "Tsuen Wan District",
          str_detect(district_code, "L") ~ "Tuen Mun District",
          str_detect(district_code, "M") ~ "Yuen Long District",
          str_detect(district_code, "N") ~ "North District",
          str_detect(district_code, "P") ~ "Tai Po District",
          str_detect(district_code, "Q") ~ "Sai Kung District",
          str_detect(district_code, "R") ~ "Sha Tin District",
          str_detect(district_code, "S") ~ "Kwai Tsing District",
          str_detect(district_code, "T") ~ "Islands District",
        ) 
    ) %>%
    # add candidate name columns
    left_join(reshaped_hk_2019_disco_candid, by = "district_code")
```

# save a version for geocoding in python

```{r}
write.csv(clean_not_geocoded_2019_dsc, "/Users/jiayili/Dropbox/senior-thesis/01-code/working-data/clean_not_geocoded_2019_dsc.csv")
```

# load the geocoded data to check bad coordinates

```{r}
# load data
path_2 <- "/Users/jiayili/Dropbox/senior-thesis/01-code/working-data"
geocoded_2019_dsc <- 
  read.csv(glue("{path_2}/geocoded_hk_2019_disco.csv"))

# check for bad coordinates
not_handgeocoded_2019_dsc <-
  geocoded_2019_dsc %>%
  ##########################
  # Geographic Coordinates #
  ##########################
    mutate(
    # remove brackets in the `ps_gmaps_coords` column
      ps_gmaps_coords = str_replace_all(ps_gmaps_coords, "\\[|\\]", "")
    ) %>%
    # separate the `gmaps_coords` column into two: lat and lon
    separate(ps_gmaps_coords, into = c("lat", "lon"), sep = ",", remove = FALSE) %>%
    # check for bad coordinates
    # Hong Kong SAR lies between Latitude 22째08' North and 22째35' North, 
    # Longitude 113째49' East and 114째31' East
    mutate(
      bad_coords =
        case_when(
          as.numeric(lat) < 22|as.numeric(lat) > 23|as.numeric(lon) < 113|as.numeric(lon) > 115 ~ "bad",
          TRUE ~ "good"
        )
    )
```

# reorder the columns

```{r}
# set the order
  col_order <-
    c("constituency",
      "district_name",
      "district_code",
      "chinese_name",
      "station_code",
      "name_poll_station",
      "chinese_name_poll_station",
      "ps_gmaps_coords",
      "lat",
      "lon",
      "bad_coords",
      "name_candid_1",
      "votes_candidate_1",
      "name_candid_2",
      "votes_candidate_2",
      "name_candid_3",
      "votes_candidate_3",
      "name_candid_4",
      "votes_candidate_4",
      "name_candid_5",
      "votes_candidate_5",
      "votes_candidate_6"
    )
# reorder the columns
  not_handgeocoded_2019_dsc <- 
    not_handgeocoded_2019_dsc[, col_order] %>%
    # drop `votes_candidate_6`: no candidate
    select(-votes_candidate_6)
```

# save a version for hand geocoding
```{r}
write.csv(not_handgeocoded_2019_dsc, "clean_not_handgeocoded_2019_disco.csv")
```

# randomly sample a portion for auditing: 10 percent

```{r}
set.seed(123)
audit_10p_2019_disco <-
    not_handgeocoded_2019_dsc %>%
    # drop those i manually corrected
    filter(bad_coords != "bad") %>%
    # sample ten percent of polling stations for auditing
    sample_n(61)
```

