---
title: "Cleaning the 2016 Legislative Council Election Data"
author: "Jiayi Li"
date: "2023-01-02"
output: html_document
---
Purpose: to clean the election results of the 2016 Legislative Council Election.

Notes: 1. the electoral rule in 2012 --> PR (Hare quota); 2. the polling station starting with LC for each large constituency (Asia Expo) is used for placing misplaced ballots. 

```{r}
# load packages
source("helper-packages.R")

# load raw election data
path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2012_legislative_council_election/individual_stations"

# get file names
data_files <- list.files(path, full.names = TRUE)

# loop in all file names to load data
for(i in 1:length(data_files)) {                              
  assign(paste0("hk_2012_legco_", i),                                  
         rio::import(data_files[i]))
}

# load data for candidate lists and political affiliations
path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2012_legislative_council_election"

party_candidate_lists <-
  read.csv(glue("{path}/2012_legco_candidate_list.csv"))

poli_affiliations <-
  read.csv(glue("{path}/legco_2012_party_candidate_info.csv"), 
           na.strings = "NA_character")
```

# clean and reshape the candidate lists and political affiliations

```{r}
joined_candidate_list <-
  party_candidate_lists %>%
  left_join(poli_affiliations, by = c("lc_code", "list_number")) %>%
  group_by(lc_code, list_number, votes_received, party_allegiance, poli_ideo) %>%
  summarise(
    candidate_names = paste(candidates, collapse = ',')
  ) %>%
  pivot_wider(
    id_cols = "lc_code",
    names_from = "list_number",
    values_from = c("candidate_names", "party_allegiance", "poli_ideo")
  )
```

# stack all election result files

```{r}
# bind rows 
stacked_2012_legco <-
  # merge all loaded data sets
  do.call("rbind", mget(ls(pattern = "^hk_2012_legco_*")))

# reset index
row.names(stacked_2012_legco) <- NULL
```

# clean the stcaked file

```{r}
# cleaning and adding party affiliations for each list
stacked_cleaned_2012_legco <-
  stacked_2012_legco %>%
  mutate(
    # adding general info
    year = "2012",
    
    election_type = "Legislative Council Election",
    
    electoral_rule = "Proportional representation",
    
    ################
    # Constituency #
    ################
    
    # add a broad geographical constituency: character (higher)
    lc_constituency = 
      case_when(
         lc_code == "LC1" ~ "Hong Kong Island",
         lc_code == "LC2" ~ "Kowloon West", 
         lc_code == "LC3" ~ "Kowloon East", 
         lc_code == "LC4" ~ "New Territories West", 
         lc_code == "LC5" ~ "New Territories East", 
      ),
    
    # add a lower geographical constituency: character
    lower_constituency = 
      case_when(
        # drop Asia Expo (used for counting misplaced ballots)
        id_poll_station %in% c("LC001", "LC002", "LC003", "LC004", "LC005") ~ NA_character_,
        str_detect(id_poll_station, "^A") ~ "Central & Western",
        str_detect(id_poll_station, "^B") ~ "Wan Chai",
        str_detect(id_poll_station, "^C") ~ "Eastern District",
        str_detect(id_poll_station, "^D") ~ "Southern District",
        str_detect(id_poll_station, "^E") ~ "Yau Tsim Mong District",
        str_detect(id_poll_station, "^F") ~ "Sham Shui Po",
        str_detect(id_poll_station, "^G") ~ "Kowloon City District",
        str_detect(id_poll_station, "^H") ~ "Wong Tai Sin District",
        str_detect(id_poll_station, "^J") ~ "Kwun Tong District",
        str_detect(id_poll_station, "^K") ~ "Tsuen Wan District",
        str_detect(id_poll_station, "^L") ~ "Tuen Mun District",
        str_detect(id_poll_station, "^M") ~ "Yuen Long District",
        str_detect(id_poll_station, "^S") ~ "Kwai Tsing District",
        str_detect(id_poll_station, "^T") ~ "Islands District",
        str_detect(id_poll_station, "^N") ~ "North District",
        str_detect(id_poll_station, "^P") ~ "Tai Po District",
        str_detect(id_poll_station, "^Q") ~ "Sai Kung District",
        str_detect(id_poll_station, "^R") ~ "Sha Tin District")
  ) %>%
  # join the party affiliations for each list
  left_join(joined_candidate_list, by = "lc_code") 
```

# save a version for geocoding

```{r}
write.csv(stacked_cleaned_2012_legco,
          glue("{path}/clean_not_geocoded_2012_legco.csv"),
          row.names = FALSE)
```

# load the geocoded file

```{r}
geocoded_legco_2012 <-
  read.csv(glue("{path}/geocoded_legco_2012.csv"),
           na.strings = c("", NA_character_))
```

# clean the geocoded file

```{r}
cleaned_geocoded_legco_2012 <-
  geocoded_legco_2012 %>%
  rename("ps_gmaps_coords" = gmaps_coords) %>%
  mutate(
    # remove brackets in the `ps_gmaps_coords` column
    ps_gmaps_coords = str_replace_all(ps_gmaps_coords, "\\[|\\]", "")
  ) %>%
  # separate the `gmaps_coords` column into two: lat and lon
  separate(ps_gmaps_coords, into = c("lat", "lon"), sep = ",", remove = FALSE) %>%
  # check for bad coordinates
  # Hong Kong SAR lies between Latitude 22째08' North and 22째35' North, 
  # Longitude 113째49' East and 114째31' East
  mutate(
    bad_coords =
      case_when(
        as.numeric(lat) < 22|as.numeric(lat) > 23|as.numeric(lon) < 113|as.numeric(lon) > 115 ~ "bad",
        TRUE ~ "good"
      )
  ) %>%
  # remove `bad names`
  select(-bad_names) %>%
  # standardize district names
  mutate(
    lower_constituency =
      case_when(
        lower_constituency %in% c("Central & Western", "Wan Chai", "Sham Shui Po") ~ paste(lower_constituency, "District"),
        TRUE ~ as.character(lower_constituency)
      )
  ) %>%
  # reorder the columns
  select(
    year,
    election_type,
    electoral_rule,
    lc_constituency,
    lc_code,
    lower_constituency,
    id_poll_station,
    chinese_name_poll_station,
    english_name_poll_station,
    ps_gmaps_coords,
    lat,
    lon,
    bad_coords,
    starts_with("list_"),
    total,
    starts_with("poli_ideo_"),
    starts_with("candidate_names_"),
    starts_with("party_allegiance_"),
  )
```

# save a version for geocoding by hand

```{r}
write.csv(cleaned_geocoded_legco_2012, 
          glue("{path}/handcoding_clean_geocoded_2012_legco.csv"),
          row.names = FALSE)
```

# randomly select a sample for auditing (drop `bad_coords` == bad)

```{r}
set.seed(123)
audit_10p_2012_legco <-
    cleaned_geocoded_legco_2012 %>%
    # drop those i manually corrected
    filter(bad_coords != "bad") %>%
    # sample ten percent of polling stations for auditing
    sample_n(55)
```


