---
title: "Cleaning Party Candidate Info for HK Elections"
author: "Jiayi Li"
date: "2022-12-24"
output: html_document
---

Purpose: to clean the party candidate info for elections between 2011 and 2021.

```{r}
# load packages
source("helper-packages.R")
```

# 2011 Disco
# Notes: Party affiliations are not available from the gov's website anymore --> scraped from wikipedia archives. Note that the info for 2011 is only available in Chinese and requires translations. (Source: https://tinyurl.com/2hanp5y5)

```{r}
##########
## 2011 ##
##########

# load raw data
  path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election/party-candidate-info"

# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("party_2011_disco_", i),                                   
           read.csv(data_files[i]))
  }
  
# load data for english candidate names and constituency names
# source: HKSAR gov website
  raw_eng_candid <-
    rio::import("~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election/2011_DCE_Valid_Nominations_E.xls") %>%
    rename("District_Code" = "DCCA Code",
           "Candidate_Number" = "Candidate No.",
           "Candidate_Name_Eng" = "Name") %>%
    # drop alias
    select(-Alias)
```

# stack all data files

```{r}
stacked_raw <-
    # merge all loaded data sets
    do.call("rbind", mget(ls(pattern = "^party_2011_disco_*")))

# reset index
row.names(stacked_raw) <- NULL
```

# get unique affiliation names and save it for hand-coding (pro-democracy/pro-establishment)

```{r}
ls_uni_affiliations <-
  stacked_raw %>%
  distinct(`政治聯繫`)

#write_csv(ls_uni_affiliations, "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election/poli_affiliations_2011.csv")
```

# load the handcoded file for political affiliations

```{r}
poli_affi_2011 <-
  rio::import("~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election/poli_affiliations_2011.xlsx")
```


# cleaning and translation

```{r}
stacked_clean <- 
  stacked_raw %>%
  # translate column names to english
  rename("District_Code" = "選區號碼",
         "Chinese_Name" = "選區",
         "Candidate_Name_Chinese" = "候選人姓名",
         "Alias" = "別名",
         "Political_Affiliations" = "政治聯繫") %>%
  mutate(
    # parse candidate numbers for each constituency district
    Candidate_Number =
      case_when(
        str_detect(Candidate_Name_Chinese, "^1.") ~ "1",
        str_detect(Candidate_Name_Chinese, "^2.") ~ "2",
        str_detect(Candidate_Name_Chinese, "^3.") ~ "3",
        str_detect(Candidate_Name_Chinese, "^4.") ~ "4",
        str_detect(Candidate_Name_Chinese, "^5.") ~ "5",
        str_detect(Candidate_Name_Chinese, "^6.") ~ "6",
        TRUE ~ NA_character_
      )
  ) %>%
  # add english translations for candidate names and district names
  left_join(raw_eng_candid, by = c("District_Code", "Candidate_Number")) %>%
  # add political affiliations
  left_join(poli_affi_2011, by = "Political_Affiliations")
```

# save to csv

```{r}
write.csv(stacked_clean, "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2011_district_council_election/stacked_party_candidate_info_2011_disco.csv", row.names = FALSE)
```



# 2015 Disco 

```{r}
##########
## 2015 ##
##########

# load raw data
  path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2015_district_council_election/party-candidate-info"

# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("party_2015_disco_", i),                                   
           read.csv(data_files[i]))
  }
```

# stack all data files

```{r}
stacked_raw <-
    # merge all loaded data sets
    do.call("rbind", mget(ls(pattern = "^party_2015_disco_*")))

# reset index
row.names(stacked_raw) <- NULL
```

# save to csv

```{r}
write.csv(stacked_raw, "/Users/jiayili/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2015_district_council_election/stacked_party_candidate_info_2015_disco.csv")
```


# 2019 Disco 

```{r}
##########
## 2019 ##
##########

#rm(list = ls())

# load raw data
  path <- "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2019_district_council_election/party-candidate-info"

# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("party_2019_disco_", i),                                   
           read.csv(data_files[i]))
  }
```

# stack all data files

```{r}
stacked_raw <-
  # if prescribed body 3 is not NA, the column type is different
  # can't use `do.call`
  party_2019_disco_1 %>%
  bind_rows(party_2019_disco_2) %>%
  bind_rows(party_2019_disco_3) %>%
  bind_rows(party_2019_disco_4) %>%
  bind_rows(party_2019_disco_5) %>%
  bind_rows(party_2019_disco_6) %>%
  bind_rows(party_2019_disco_7) %>%
  bind_rows(party_2019_disco_8) %>%
  bind_rows(party_2019_disco_9) %>%
  bind_rows(party_2019_disco_10) %>%
  bind_rows(party_2019_disco_11) %>%
  bind_rows(party_2019_disco_12) %>%
  bind_rows(party_2019_disco_13) %>%
  bind_rows(party_2019_disco_14) %>%
  bind_rows(party_2019_disco_15) %>%
  bind_rows(party_2019_disco_16) %>%
  bind_rows(party_2019_disco_17) %>%
  bind_rows(party_2019_disco_18) %>%
  # cleaning: combine info from columns created due to non-standardized column names
  mutate(
    `INDEPENDENT.CANDIDATE...NON.AFFILIATED.CANDIDATE` = 
      case_when(
        `INDEPENDENT.CANDIDATE....NON.AFFILIATED.CANDIDATE` %in% c("INDEPENDENT CANDIDATE", "NON-AFFILIATED CANDIDATE", "NA") ~ as.character(INDEPENDENT.CANDIDATE....NON.AFFILIATED.CANDIDATE),
        `INDEPENDENT.CANDIDATE...NON.AFFILIATED` %in% c("INDEPENDENT CANDIDATE", "NON-AFFILIATED CANDIDATE", "NA") ~ as.character(INDEPENDENT.CANDIDATE...NON.AFFILIATED),
        `INDEPENDENT.CANDIDATE.NON.AFFILIATED` %in% c("INDEPENDENT CANDIDATE", "NON-AFFILIATED CANDIDATE", "NA") ~ as.character(INDEPENDENT.CANDIDATE.NON.AFFILIATED),
        TRUE ~ as.character(INDEPENDENT.CANDIDATE...NON.AFFILIATED.CANDIDATE)
      )
  )  %>%
  # remove those unwanted columns
  select(-INDEPENDENT.CANDIDATE....NON.AFFILIATED.CANDIDATE) %>%
  select(-INDEPENDENT.CANDIDATE...NON.AFFILIATED) %>%
  select(-INDEPENDENT.CANDIDATE.NON.AFFILIATED)
```


# save a csv

```{r}
write.csv(stacked_raw, "~/Desktop/honors-thesis-main/00-data/raw-data/raw-election-data/2019_district_council_election/stacked_party_candidate_info_2019_disco.csv")
```

