---
title: "Cleaning 2016 HK Legislative Council Election Data"
author: "Jiayi Li"
date: "2022-08-24"
output: html_document
---
Purpose: to clean the election results of 2016 HK LegCo Election.
** Not hand-geocoded yet **
To-Do:
- 08/24/2022:
  -- Merge all excel files (done)
  -- Add constituency variables (done)
  -- Geocode the merged file in Python (done)
  -- Break coordinates of polling stations into two columns and check for bad coordinates (done)
  -- Reorder columns (done)
- 08/27/2022:
  -- Add candidate name columns 
  
```{r setup, include=FALSE}
rm(list = ls())
knitr::opts_chunk$set(echo = TRUE)
```

# load packages and raw data

```{r}
# load packages
  source("../helper-packages.R")

# load raw election data
  path <- "/Users/jiayili/Dropbox/senior-thesis/00-data/00-raw-data/election-data/2016_legislative_council_election/individual_stations"
# get file names
  data_files <- list.files(path, full.names = TRUE)
  
# loop in all file names to load data
  for(i in 1:length(data_files)) {                              
    assign(paste0("hk_2016_legco_", i),                                  
           rio::import(data_files[i]))
  }
  
# load candidate lists
  path_candid_list <- "/Users/jiayili/Dropbox/senior-thesis/00-data/00-raw-data/election-data/2016_legislative_council_election"
  candid_list_2016_raw <-
    rio::import(glue("{path_candid_list}/2016_legco_candidate_list.csv"))
```

# stack all excel files

```{r}
# bind rows 
  hk_2016_lce_raw <-
    # merge all loaded data sets
    do.call("rbind", mget(ls(pattern = "^hk_2016_legco_*")))
# reset index
  row.names(hk_2016_lce_raw) <- NULL
```

# reshape the candidate list for matching

```{r}
# pivot wider
  # reshaped_candid_list_2016 <-
  #   candid_list_2016_raw %>%
  #   mutate(
  #     
  #   ) %>%
  #   pivot_wider(
  #   id_cols = `lc_code`,
  #   names_from = `list_number`,
  #   values_from = `votes_received`,
  #   names_prefix = "list_candid_"
  #   )
```


# clean

```{r}
# clean
clean_not_geocoded_2016_lce <-
  hk_2016_lce_raw %>%
  mutate(
    election = "2016 Legislative Council Election", 
    
    ################
    # Constituency #
    ################
    
    # add a broad geographical constituency: character (higher)
    lc_constituency = 
      case_when(
         lc_code == "LC1" ~ "Hong Kong Island",
         lc_code == "LC2" ~ "Kowloon West", 
         lc_code == "LC3" ~ "Kowloon East", 
         lc_code == "LC4" ~ "New Territories West", 
         lc_code == "LC5" ~ "New Territories East", 
      ),
    
    # add a lower geographical constituency: character
    lower_constituency = 
      case_when(
        # drop Asia Expo (used for counting misplaced ballots)
        id_poll_station %in% c("LC001", "LC002", "LC003", "LC004", "LC005") ~ NA_character_,
        str_detect(id_poll_station, "^A") ~ "Central & Western",
        str_detect(id_poll_station, "^B") ~ "Wan Chai",
        str_detect(id_poll_station, "^C") ~ "Eastern District",
        str_detect(id_poll_station, "^D") ~ "Southern District",
        str_detect(id_poll_station, "^E") ~ "Yau Tsim Mong District",
        str_detect(id_poll_station, "^F") ~ "Sham Shui Po",
        str_detect(id_poll_station, "^G") ~ "Kowloon City District",
        str_detect(id_poll_station, "^H") ~ "Wong Tai Sin District",
        str_detect(id_poll_station, "^J") ~ "Kwun Tong District",
        str_detect(id_poll_station, "^K") ~ "Tsuen Wan District",
        str_detect(id_poll_station, "^L") ~ "Tuen Mun District",
        str_detect(id_poll_station, "^M") ~ "Yuen Long District",
        str_detect(id_poll_station, "^S") ~ "Kwai Tsing District",
        str_detect(id_poll_station, "^T") ~ "Islands District",
        str_detect(id_poll_station, "^N") ~ "North District",
        str_detect(id_poll_station, "^P") ~ "Tai Po District",
        str_detect(id_poll_station, "^Q") ~ "Sai Kung District",
        str_detect(id_poll_station, "^R") ~ "Sha Tin District"
      )
  )

# rename the legislative council constituency code column
names(clean_not_geocoded_2016_lce$lc_code) <- "lc_constituency_code"
```

# save a version for geocoding in python

```{r}
write.csv(clean_not_geocoded_2016_lce, "/Users/jiayili/Dropbox/senior-thesis/01-code/01-data-cleaning/election-data/clean_not_geocoded_2016_lce.csv")
```

# load the geocoded data

```{r}
path_work_dat <- "/Users/jiayili/Dropbox/senior-thesis/01-code/01-data-cleaning/election-data"

geocoded_2016_lce <-
  read.csv(glue("{path_work_dat}/geocoded_hk_2016_legco.csv"))
```

# clean the geocoded data

```{r}
not_handgeocoded_2016_lce <-
  geocoded_2016_lce %>%
  ##########################
  # Geographic Coordinates #
  ##########################
    mutate(
    # remove brackets in the `ps_gmaps_coords` column
      ps_gmaps_coords = str_replace_all(ps_gmaps_coords, "\\[|\\]", "")
    ) %>%
    # separate the `gmaps_coords` column into two: lat and lon
    separate(ps_gmaps_coords, into = c("lat", "lon"), sep = ",", remove = FALSE) %>%
    # check for bad coordinates
    # Hong Kong SAR lies between Latitude 22째08' North and 22째35' North, 
    # Longitude 113째49' East and 114째31' East
    mutate(
      bad_coords =
        case_when(
          as.numeric(lat) < 22|as.numeric(lat) > 23|as.numeric(lon) < 113|as.numeric(lon) > 115 ~ "bad",
          TRUE ~ "good"
        )
    )
```

# reorder the columns

```{r}
not_handgeocoded_2016_lce <-
  not_handgeocoded_2016_lce %>%
  select(
    election,
    lc_constituency,
    lc_constituency_code = lc_code,
    lower_constituency,
    id_poll_station,
    chinese_name_poll_station,
    english_name_poll_station,
    ps_gmaps_coords,
    lat,
    lon,
    bad_coords,
    starts_with("list_"),
    total
  )
```

# save a version for hand geocoding

```{r}
write.csv(not_handgeocoded_2016_lce, "/Users/jiayili/Dropbox/senior-thesis/01-code/01-data-cleaning/election-data/not_handgeocoded_2016_lce.csv")
```

